\label{chap:proposed_endeavor}

\section{Overview}
The applicant proposes a multi-year initiative focused on financial system resilience through advanced AI, open-source research, and workforce development. \textbf{It is important to note that all cited publications throughout this proposal are the original work of the applicant, Mr. Satyadhar Joshi, published under his name in peer-reviewed journals and academic platforms.} These publications demonstrate his ongoing progress and established thought leadership in the field, forming the foundation for his proposed future endeavors. The following sections detail the activities, timelines, and projected deliverables building upon this substantial body of existing work.


\section{Initiative 1: Advancing Agentic Gen AI in Financial and Economic Risk}
\begin{itemize}
	\item Develop generative AI models for stress testing and monitoring U.S. financial institutions to enhance economic stability.\footnote{S. Joshi, ``Review of Gen AI Models for Financial Risk Management: Architectural Frameworks and Implementation Strategies,'' \textit{Preprints.org}, May 2, 2025. doi: 10.20944/preprints202505.0054.v1.}
	\item Implement real-time risk monitoring using big data platforms such as Hadoop and Spark for financial decision support.\footnote{S. Joshi, ``Review of Data Pipelines and Streaming for Generative AI Integration: Challenges, Solutions, and Future Directions,'' \textit{International Journal of Research Publication and Reviews}, vol. 6, no. 2, pp. 89-104, Feb. 1, 2025. doi: 10.55248/ijrpr.2025.6.2.124.}
	\item Enhance Gen AI implementation, oversight, and regulation in the U.S. healthcare domain to improve safety, compliance, and operational efficiency.\footnote{S. Joshi, ``A Comprehensive Review of Gen AI Agents: Applications and Frameworks in Finance, Investments and Risk Domains,'' \textit{International Journal of Innovative Science and Research Technology}, vol. 10, no. 5, pp. 1-15, May 24, 2025. doi: 10.38124/IJISRT25MAY123.}
		\item Develop generative AI applications for investment and portfolio management optimization.\footnote{S. Joshi, ``Generative AI in Investment and Portfolio Management: Comprehensive Review of Current Applications and Future Directions,'' \textit{Preprints.org}, May 8, 2025. doi: 10.20944/preprints202505.0221.v1.}
	\item Create AI-enhanced models for structured finance risk assessment and management.\footnote{S. Joshi, ``Enhancing structured finance risk models (Leland-Toft and Box-Cox) using GenAI (VAEs GANs),'' \textit{International Journal of Science and Research Archive}, vol. 15, no. 1, pp. 234-250, Jan. 30, 2025. doi: 10.30574/ijsra.2025.15.1.0045.}
	\item Implement AI-driven market resilience frameworks using generative adversarial networks and variational autoencoders.\footnote{S. Joshi, ``Using Gen AI Agents With GAE and Vecond filing is legitimate and not just a repeat.AE to Enhance Resilience of US Markets,'' \textit{International Journal of Computational Science Information Technology and Control Engineering}, vol. 12, no. 1, pp. 23-45, Jan. 28, 2025. doi: 10.30534/ijcstce/2025/121012025.}
	\item Advance prompt engineering techniques for financial market integrity and risk management.\footnote{S. Joshi, ``Leveraging prompt engineering to enhance financial market integrity and risk management,'' \textit{World Journal of Advanced Research and Reviews}, vol. 25, no. 1, pp. 100-115, Jan. 30, 2025. doi: 10.30574/wjarr.2025.25.1.0034.}
\end{itemize}

\section{Initiative 2: Open-Source Research and Knowledge Dissemination on Agentic Gen AI}
\begin{itemize}
	\item Publish peer-reviewed research on AI applications in financial risk management, healthcare, and cybersecurity for U.S. stakeholders.\footnote{S. Joshi, ``Architectures and Challenges of AI Multi-Agent Frameworks for Financial Services,'' \textit{Current Journal of Applied Science and Technology}, vol. 44, no. 6, pp. 1-15, Jun. 5, 2025. doi: 10.19080/CJAST.2025.44.556242.}
	\item Release open-source tools for regulatory compliance, risk modeling, and operational transparency across sectors.\footnote{S. Joshi, ``A Review of Generative AI and DevOps Pipelines: CI/CD, Agentic Automation, MLOps Integration, and Large Language Models,'' \textit{Preprints.org}, Jun. 12, 2025. doi: 10.20944/preprints202506.0124.v1.}
	\item Organize workshops and webinars for financial sector professionals to share best practices and advance AI adoption responsibly.\footnote{S. Joshi, ``The Role of AI in Enhancing Teamwork, Resilience and Decision-Making: Review of Recent Developments,'' \textit{International Journal of Computer Applications}, vol. 187, no. 3, pp. 23-45, May 28, 2025. doi: 10.36920/ijca.2025.187.3.012.}
\end{itemize}

\section{Initiative 3: Workforce Development and Training, Thought Leadership of Gen AI Application in Education and Health}
\begin{itemize}
	\item Create training programs for U.S. veterans and other professionals to enter AI-driven financial and technology careers.\footnote{S. Joshi, ``Retraining US Workforce in the Age of Agentic Gen AI: Role of Prompt Engineering and Up-Skilling Initiatives,'' \textit{International Journal of Advanced Research in Science, Communication and Technology}, vol. 5, no. 2, pp. 1-12, Feb. 17, 2025. doi: 10.48175/IJARSCT-23261.}
	\item Develop online courses (e.g., Gen AI Python for Health, Cyberspace, LLMs for compliance) to build AI literacy and skills in health, education, and cybersecurity domains.\footnote{S. Joshi, ``Training the US Older Workforce for the Impact of Generative AI on Financial Services: A Policy Guide,'' \textit{Preprints.org}, Apr. 8, 2025. doi: 10.20944/preprints202504.0221.v1.}
	\item Launch a non-profit initiative (CRAF) focused on financial AI policy, ethical AI adoption, and workforce upskilling in the United States.\footnote{S. Joshi, ``Strategic Integration of Artificial Intelligence in U.S. K–12 Education: A Comprehensive Review and Policy Roadmap,'' \textit{Preprints.org}, Jun. 16, 2025. doi: 10.20944/preprints202506.0164.v1.}
\end{itemize}

\section{Initiative 4: Defense and National Security Applications of AI}
\begin{itemize}
	\item Develop secure multi-party computation (SMC) protocols for military and intelligence applications enabling secure collaboration between allied forces.\footnote{R. Pathak and S. Joshi, ``Secure Multi-party Computation Protocol for Defense Applications in Military Operations Using Virtual Cryptography,'' in \textit{Contemporary Computing}, S. Ranka et al., Eds., Berlin, Heidelberg: Springer, 2009, pp. 389–399. doi: 10.1007/978-3-642-03547-0\_37.}
	\item Advance Agentic AI and High-Performance Computing (HPC) systems for proactive cyber defense of critical infrastructure.\footnote{S. Joshi, ``Advancing Cybersecurity Through Synergies of Agentic AI and High-Performance Computing,'' vol. 02, no. 07, 2025. doi: 10.20944/preprints202507.0124.v1.}
	\item Create AI-driven threat detection frameworks for military command and control systems protection.\footnote{S. Joshi, ``Gen AI in Financial Cybersecurity: A Comprehensive Review of Architectures, Algorithms, and Regulatory Challenges,'' \textit{International Journal of Innovations in Science, Engineering And Management}, pp. 73–88, July 2025. doi: 10.69968/ijisem.2025v4i373-88.}
	\item Develop specialized training programs for defense personnel in AI security applications and cyber warfare preparedness.\footnote{S. Joshi, ``The Impact of AI on Veteran Employment and the Future Workforce Development: Opportunities, Barriers, and Systemic Solutions,'' \textit{World J. Adv. Res. Rev.}, vol. 27, no. 2, pp. 328–341, Sept. 2025. doi: 10.30574/wjarr.2025.27.3.3147.}
\end{itemize}

\section{Initiative 5: Advanced AI Research and Technical Innovation}
\begin{itemize}
	\item Conduct foundational research on Artificial General Intelligence (AGI) and its applications in business and finance.\footnote{S. Joshi, ``Comprehensive Review of Artificial General Intelligence AGI and Agentic GenAI: Applications in Business and Finance,'' \textit{Preprints.org}, May 12, 2025. doi: 10.20944/preprints202505.0287.v1.}
	\item Develop mitigation strategies for AI model weaknesses and hallucinations in critical financial applications.\footnote{S. Joshi, ``Mitigating LLM Hallucinations: A Comprehensive Review of Techniques and Architectures,'' \textit{Preprints.org}, May 26, 2025. doi: 10.20944/preprints202505.0421.v1.}
	\item Create advanced AI leadership frameworks for organizational decision-making and strategic planning.\footnote{S. Joshi, ``Leadership in the Age of AI: Review of Quantitative Models and Visualization for Managerial Decision-Making,'' \textit{Preprints.org}, Apr. 21, 2025. doi: 10.20944/preprints202504.0421.v1.}
	\item Investigate AI applications in conflict resolution and emotional intelligence for enhanced organizational effectiveness.\footnote{S. Joshi, ``Artificial Intelligence in Conflict Resolution: A Comprehensive Review of Techniques and Applications,'' \textit{Preprints.org}, May 7, 2025. doi: 10.20944/preprints202505.0187.v1.}
\end{itemize}


\section{Nonprofit Startup Endeavor and Relevant Expertise}

\subsection{International Startup MBA in Israel and Current Location in NYC}

With an International MBA from Bar-Ilan University in Israel, Mr. Joshi brings a global perspective essential for advancing interdisciplinary research and nonprofit development. The program included rigorous coursework in accounting, finance, and marketing, with particular emphasis on startup organizations, nonprofit enterprises, and funding strategies.  

This training provides a solid foundation in financial management, strategic marketing, and operational planning—skills critical for establishing and leading a nonprofit dedicated to responsible AI innovation and workforce development. Coupled with his interdisciplinary scientific expertise, this MBA background uniquely equips Mr. Joshi to design and implement effective strategies for organizational registration, accounting, marketing, financial planning, pitching, and fundraising.  

Residing in New York City, Mr. Joshi actively participates in professional meetups and industry gatherings, which expose him to cutting-edge ideas and best practices in nonprofit management and sector collaborations. These experiences enhance his understanding of sustainable nonprofit strategies and expand his professional network, positioning him to implement impactful initiatives aligned with national priorities.  

His international education further enables him to navigate cross-border collaborations and foster public–private partnerships, amplifying the global impact of nonprofit initiatives. This combination of scientific insight and business acumen demonstrates that Mr. Joshi’s nonprofit plans are both feasible and strategically sound, with the potential for substantial public benefit and alignment with the national interest.




\section{Five-Year Timeline and Milestones}
\begin{longtable}{|p{0.18\textwidth}|p{0.30\textwidth}|p{0.46\textwidth}|}
	\hline
	\textbf{Year} & \textbf{Key Activities} & \textbf{Projected Outcomes} \\
	\hline
	2026 & Launch CRAF non-profit initiative, implement AI risk tools, begin defense SMC protocol development & 5,000+ course registrations, 500+ veterans enrolled, initial defense framework prototype \\
	\hline
	2027 & Publish ``State of AI'' report, deploy risk adoption tools, advance Agentic AI for cyber defense & 20\% drop in risk loss, 10,000+ downloads, DOD collaboration initiated \\
	\hline
	2028 & Veteran AI fellowship, automate compliance, deploy military threat detection systems & 15,000+ MOOC enrollments, 30\% cost reduction, 2+ defense agency partnerships \\
	\hline
	2029 & AI audit toolkit, policy papers, chatbots, nationwide defense AI training & Use by 2+ federal agencies, 20,000+ trainees, defense workforce certification program \\
	\hline
	2030 & Nationwide bootcamp expansion, predictive analytics, critical infrastructure protection systems & 1,000+ veterans trained, 15\% lower defaults, national security AI framework deployment \\
	\hline
\end{longtable}

% Add more details as needed; avoid policy arguments or impact statements here.

Mr. Joshi's proposed endeavor focuses on four integrated components that collectively address critical national needs:

\subsection{Advancing Agentic Gen AI System Resilience through AI}
Mr. Joshi will continue developing and implementing advanced AI and machine learning models to enhance risk management capabilities at U.S. financial institutions by migration to his proposed Policy Research Research. His work specifically addresses:
\begin{itemize}
	\item Development of generative AI models for stress testing and scenario analysis
	\item Real-time risk monitoring systems using big data technologies (Hadoop, Spark, Kafka)
	\item Enhanced agentic risk detection and prevention frameworks
	\item Improving model accuracy and reducing operational risks in systemic financial institutions
\end{itemize}

\subsection{Research and Knowledge Dissemination}
Mr. Joshi will continue his scholarly contributions through:
\begin{itemize}
	\item Publication of peer-reviewed research on AI applications in finance
	\item Development of open-source tools for risk modeling and regulatory compliance
	\item Sharing best practices and innovations with the broader financial and regulatory community
\end{itemize}

\subsection{Workforce Development and Education}
Mr. Joshi is committed to enhancing U.S. workforce capabilities through:
\begin{itemize}
	\item Creating educational resources and training programs in financial analytics and AI
	\item Establishing specialized training initiatives for U.S. veterans transitioning to financial technology careers
	\item Developing accessible online courses and materials to upskill American professionals 
\end{itemize}

\subsection{Defense and National Security Applications}
Mr. Joshi will apply his expertise to critical national security challenges through:
\begin{itemize}
	\item Developing secure computation protocols for military and intelligence applications
	\item Creating AI-driven cyber defense systems for critical infrastructure protection
	\item Establishing training programs for defense personnel in AI security applications
	\item Supporting DOD and DHS initiatives in advanced threat detection and response
\end{itemize}

\section{Substantial Merit and National Importance}

\subsection{Alignment with National Priorities}
Mr. Joshi's work addresses several areas of critical national importance:

\subsubsection{Agentic Gen AI System Stability for Finance, Economics and Health}
The stability of the U.S. financial system is a matter of paramount national importance. Mr. Joshi's work developing advanced risk models directly supports this priority by:
\begin{itemize}
	\item Enhancing the accuracy of risk assessments for major financial institutions
	\item Reducing systemic risks of Agentic Gen AI risk adoption through better predictive modeling
	\item Supporting the mandates of the Financial Stability Oversight Council (FSOC) and U.S. Treasury Department
\end{itemize}

\subsubsection{Technological Innovation and Business Leadership}
The United States has identified leadership in artificial intelligence and big data technologies as a strategic national priority. Mr. Joshi's work contributes to this leadership by:
\begin{itemize}
	\item Applying cutting-edge AI techniques to solve practical financial challenges
	\item Developing innovative approaches to data analysis and model validation
	\item Enhancing the competitiveness of U.S. leadership institutions in global markets
	\item Supporting initiatives outlined in the White House's Executive Order on AI (Oct. 2023)
\end{itemize}

\subsubsection{Workforce Development}
Developing a skilled workforce capable of implementing advanced technologies is essential for national economic competitiveness. Mr. Joshi's educational initiatives address this need by:
\begin{itemize}
	\item Providing specialized training in high-demand technical skills
	\item Creating pathways for veterans to transition to civilian careers in technology
	\item Addressing skills gaps in the financial technology sector
	\item Supporting Department of Labor workforce development goals
\end{itemize}

\subsubsection{National Security and Defense}
The protection of U.S. national security interests through advanced technology is a fundamental government priority. Mr. Joshi's defense-focused work supports this by:
\begin{itemize}
	\item Enhancing military and intelligence capabilities through secure AI systems
	\item Protecting critical infrastructure from cyber threats using advanced AI detection
	\item Supporting DOD and DHS strategic technology initiatives
	\item Strengthening national security through innovative AI applications
\end{itemize}

\subsection{Evidence of Impact and Recognition}

\subsubsection{Professional Impact}
Mr. Joshi's work has demonstrated tangible benefits to U.S. financial institutions:
\begin{itemize}
	\item Developed quantitative models managing hundreds of billions of dollars in assets at Bank of America
	\item Implemented automation processes that reduced errors by 30-50\% at Wells Fargo
	\item Created risk assessment frameworks that enabled preemptive actions during volatile market conditions
	\item Received strong endorsements from industry leaders and supervisors 
\end{itemize}

\subsubsection{Defense and Security Contributions}
Mr. Joshi's research has direct applications to national security:
\begin{itemize}
	\item Developed secure multi-party computation protocols with military applications\footnote{R. Pathak and S. Joshi, ``Secure Multi-party Computation Protocol for Defense Applications in Military Operations Using Virtual Cryptography,'' in \textit{Contemporary Computing}, S. Ranka et al., Eds., Berlin, Heidelberg: Springer, 2009, pp. 389–399. doi: 10.1007/978-3-642-03547-0\_37.}
	\item Published advanced cybersecurity frameworks using Agentic AI and HPC\footnote{S. Joshi, ``Advancing Cybersecurity Through Synergies of Agentic AI and High-Performance Computing,'' vol. 02, no. 07, 2025.}
	\item Analyzed defense partnerships and technology transfer patterns\footnote{A. Ludhiyani and S. Joshi, ``India – Israel Defense Relationship: Quantitative \& Qualitative Analysis of Defense Companies of India and Israel,'' \textit{Journal of Defense Studies and Resource Management}, vol. 2015, May 2016. doi: 10.4172/2324-9315.1000120.}
\end{itemize}

\section{Future Plans and Projected Impact}

Mr. Joshi has developed detailed plans for advancing his proposed endeavor over the next five years, with specific metrics for measuring impact.

\subsection{Research and Development Goals}
\begin{longtable}{|p{0.3\textwidth}|p{0.65\textwidth}|}
	\hline
	\textbf{Objective} & \textbf{Metrics and Impact} \\
	\hline
	\textbf{Peer-Reviewed Publications} & 
	\begin{itemize}
		\item Publish 3-4 papers annually in high-quality journals
		\item Focus areas: Generative AI for finance, real-time risk monitoring, adversarial robustness in financial models
		\item Target 20-30 paper reviews annually for peer journals
	\end{itemize} \\
	\hline
	\textbf{Public Policy Impact} & 
	\begin{itemize}
		\item Maintain 10,000-20,000 monthly downloads of policy materials
		\item Expand repository to include regulatory sandbox frameworks, AI fairness toolkits, stress testing methodologies
		\item Partner with research institutions on white papers
	\end{itemize} \\
	\hline
	\textbf{Defense and Security Research} & 
	\begin{itemize}
		\item Develop 2-3 defense-specific AI applications annually
		\item Collaborate with DOD and DHS on threat detection systems
		\item Publish research on AI applications for national security
	\end{itemize} \\
	\hline
\end{longtable}

\subsection{Workforce Development Initiatives}
\begin{longtable}{|p{0.3\textwidth}|p{0.65\textwidth}|}
	\hline
	\textbf{Program} & \textbf{Projected Growth} \\
	\hline
	\textbf{Veterans in Financial AI} & 
	\begin{itemize}
		\item Scale from current 1,000 to 10,000+ learners by 2030
		\item Launch 3 new certification tracks: GenAI for AML compliance, Agentic AI for efficiency, Python for Agentic AI Edge AI
		\item Secure DOL/VA funding for national expansion
	\end{itemize} \\
	\hline
	\textbf{Open Courseware} & 
	\begin{itemize}
		\item Grow registrations significantly
		\item Develop integrated curricula: Python for quant finance (2026), LLM prompt engineering (2027), synthetic data generation (2028)
	\end{itemize} \\
	\hline
	\textbf{Defense AI Training} & 
	\begin{itemize}
		\item Train 500+ defense personnel annually by 2030
		\item Develop specialized courses for military AI applications
		\item Partner with defense contractors and government agencies
	\end{itemize} \\
	\hline
\end{longtable}

\subsection{Five-Year Impact Projection}
\begin{longtable}{|p{0.12\textwidth}|p{0.43\textwidth}|p{0.38\textwidth}|}
	\hline
	\textbf{Year} & \textbf{Key Initiatives} & \textbf{Projected Outcomes} \\
	\hline
	\textbf{2026} & 
	\begin{itemize}
		\item Launch Center for Responsible AI in Finance (CRAF)
		\item Publish 4 peer-reviewed papers
		\item Release AI for Financial Risk Management course
		\item Implement AI-based credit risk tools at Bank of America
		\item Begin defense SMC protocol development
	\end{itemize} & 
	\begin{itemize}
		\item 5,000+ course registrations
		\item 15\% improvement in model accuracy
		\item 500+ veterans enrolled
		\item Initial defense framework prototype
	\end{itemize} \\
	\hline
	
	\textbf{2027} & 
	\begin{itemize}
		\item Publish State of AI in U.S. Finance report
		\item Deploy fraud detection models
		\item Develop AI Agents in Banking workshops
		\item Launch open-source tools with regulators
		\item Advance Agentic AI for cyber defense
	\end{itemize} & 
	\begin{itemize}
		\item 20\% reduction in fraud losses
		\item 10,000+ paper downloads
		\item 3 community bank partnerships
		\item DOD collaboration initiated
	\end{itemize} \\
	\hline
	
	\textbf{2028} & 
	\begin{itemize}
		\item Establish veteran fellowship for AI finance
		\item Launch AGI credit risk MOOC
		\item Automate compliance monitoring
		\item Publish 2 papers on AI adoption in Risk
		\item Deploy military threat detection systems
	\end{itemize} & 
	\begin{itemize}
		\item 100+ veteran fellows placed
		\item 30\% reduction in compliance costs
		\item 15,000+ MOOC enrollments
		\item 2+ defense agency partnerships
	\end{itemize} \\
	\hline
	
	\textbf{2029} & 
	\begin{itemize}
		\item Release AI audit toolkit for regulators
		\item Publish ethics/compliance training module
		\item Deploy customer-facing AI chatbots
		\item Submit policy paper on AI fairness in lending
		\item Nationwide defense AI training rollout
	\end{itemize} & 
	\begin{itemize}
		\item Toolkit used by 2+ federal agencies
		\item 25\% boost in customer satisfaction
		\item 20,000+ training completions
		\item Defense workforce certification program
	\end{itemize} \\
	\hline
	
	\textbf{2030} & 
	\begin{itemize}
		\item Expand veteran bootcamp nationally
		\item Deploy predictive loan default analytics
		\item Establish 2–5 regional training hubs
		\item Publish workforce retraining framework
		\item Critical infrastructure protection deployment
	\end{itemize} & 
	\begin{itemize}
		\item 1,000+ veterans trained annually
		\item 15\% drop in loan defaults
		\item Engagement with 5+ state banking associations
		\item National security AI framework deployment
	\end{itemize} \\
	\hline
\end{longtable}

\section{Conclusion}

Mr. Satyadhar Joshi represents precisely the type of high-impact professional that the EB2 National Interest Waiver was designed to benefit. His work enhancing the resilience of Agentic Gen AI based implementation for the U.S. financial system and national security infrastructure addresses matters of substantial merit and national importance. His unique qualifications and proven track record demonstrate that he is well-positioned to advance his proposed endeavor. Finally, the significant benefits his work provides to the United States outweigh the national interest in protecting U.S. workers through the labor certification process.

We respectfully request that USCIS approve this petition, recognizing that Mr. Joshi's contributions to financial stability, technological innovation, workforce development, and national security provide clear and substantial benefits to the national interest of the United States.

\section{Referencing Evidences related to this Chapter}			

\textbf{Evidence Submitted}
\begin{itemize}
	\item Independent Opinion Letters from Professors, PhD and Industry experts 
	\item Evidence demonstrating the substantial merit of the endeavor
\end{itemize}

\begin{longtable}{|p{0.3\textwidth}|p{0.65\textwidth}|}
	\hline
	\textbf{RFE Concern} & \textbf{Response and Evidences} \\
	\hline
	\endhead
	Endeavor specificity & Detailed 5 year work plan with annual milestones in four different domains including defense/national security \\	\hline
	National importance & Linking how Mr Joshi's (applicant) research address specific issues of National Importance including defense applications \\
	\hline
	Current and future impact & Downloads and Selection Citations Analysis projections including defense research citations \\ 	\hline
	Missing Independent Letters & Independent Expert Opinion and Evaluations from PhDs and Professors including defense expertise \\	\hline
	Impact Beyond Job at the Bank & Two Testimonial LOR of Open Access Research published in the last decade which goes beyond the job duties including defense publications \\	\hline
\end{longtable}

\begin{table}[h!]
	\centering
	\renewcommand{\arraystretch}{1.4}
	\begin{tabular}{|p{6cm}|p{8cm}|}
		\hline
		\textbf{Criteria Addressed} & \textbf{Supporting Expert Letters / Testimonial Letters} \\
		\hline
		Support for Five-Year Plan & See Expert Opinion by Dr Asif Exhibit~\ref{chap:exhibit_asif} and by Dr Anjum Exhibit~\ref{chap:exhibit_anjum} for details on feasibility of the proposed endeavor projections. \\
		\hline
		Evidence of Top 10\% Standing in Field & Expert Letter by Dr. Rozeria Exhibit~\ref{chap:rozeia} and by Dr Malik Exhibit~\ref{chap:exhibit_malik} \\
		\hline
		Verification of DOIs, Online Profiles, and Awards & Expert Letter by Dr Sheraz Exhibit\ref{chap:sheraz} and Dr. Kamran Exhibit~\ref{chap:exhibit_kamran} \\
		\hline
		Impact beyond employer to the overall field & Testimonial Letter by Mr. Ankit Exhibit\ref{chap:exhibit_ankit} and Mr Gaurav Exhibit~\ref{chap:exhibit_gaurav} \\
		\hline
		Defense and National Security Applications & Defense research publications and analysis of international defense partnerships demonstrating national security relevance \\
		\hline
	\end{tabular}
	\caption{Summary of Expert Opinion Letters and Supporting Evidence. Independent}
	\label{tab:expert_letters_summary}
\end{table}

Expert letters were obtained from professors with familiarity and experience regarding the EB2-NIW process. These experts were provided with the applicant's EB2-NIW petition materials, including the five-year research plan and published works. Accordingly, the experts were well-positioned to evaluate the candidate's qualifications in a comprehensive and holistic manner, and their recommendations should be considered informed and appropriate.


