





\section{EB2 National Interest Waiver (NIW) Application: Enhancing US financial resilience through Gen AI and Big Data}

\section{A. Executive Summary}

The undersigned represents \textbf{Satyadhar Joshi}, currently employed with \textbf{Bank of America} in the \textbf{Global Risk \& Analytics} division as Assistant Vice President (AVP) in Jersey City, New Jersey.

Under USCIS guidelines for the EB2 National Interest Waiver (NIW), including \textbf{8 CFR § 204.5(k)(2)} (advanced degree or equivalent), \textbf{8 CFR § 204.5(k)(3)(ii)(F)} (publications in professional journals), and \textbf{8 CFR § 204.5(k)(3)(ii)(E)} (membership in professional organizations with outstanding achievements), 10 years of professional experience, \textbf{(8 CFR § 204.5(k)(2))}, Mr. Joshi's qualifications fully satisfy the eligibility criteria.
We further submit evidence and documentation to demonstrate that a waiver of the labor certification in Mr Joshi's	case is in the national interest pursuant to In re Matter of Dhanasar, 26 IN Dec. 884 (AAO 2016), Int. Dec. 3882.
\begin{enumerate}
	\item Mr. Joshi holds advanced degrees---a Master of Science in Information Systems and an MBA [Exhibit 5], which meet the advanced degree requirement (\textbf{8 CFR § 204.5(k)(2)}).
	
	\item Further, his academic publications [Section C], reflected on \textbf{Google Scholar} and consist of over seventy scholarly  articles with over Five Hundred citations, fulfilling the publication and citation requirement (\textbf{8 CFR § 204.5(k)(3)(ii)(F)}).
	
	\item Additionally, Mr. Joshi was a member of \textbf{GAARP-FRM} (Global Association of Risk Professionals -- Financial Risk Manager) [Section D], a professional organization requiring elite qualifications (\textbf{8 CFR § 204.5(k)(3)(ii)(E)}), underscoring his exceptional ability.
	
	\item With over \textbf{10 years of total professional experience} [as shown in Section B], including \textbf{6 years at Bank of America} within the United States, Mr. Joshi's expertise in managing complex financial systems to strengthen the US economy directly aligns with national needs for advancing financial risk management, recognizing professional experience as pivotal to the U.S. economy and public interest.
\end{enumerate}

We will present a case where we will show that Mr. Joshi's work directly aligns with USCIS National Interest Waiver criteria \textbf{(8 CFR § 204.5(k))} by enhancing financial resilience through AI modeling, big data technologies, model implementation, machine learning, which support U.S. economic security. Mr. Joshi also drove innovation in financial analytics, using tools like Hadoop, Spark, and Kafka, while educating the workforce to tackle systemic challenges. These contributions align with national priorities in finance, technology, and workforce development, reinforcing Mr. Joshi's eligibility for the EB2 National Interest Waiver.

\subsection{(i) Eligibility}

Under USCIS guidelines, the \textbf{EB2 National Interest Waiver (NIW)} is available to individuals who hold an advanced degree (master's degree or higher) or possess exceptional abilities that significantly benefit the United States. Specifically, according to 8 CFR § 204.5(k)(2), eligibility for EB2 can be established by demonstrating possession of a degree above a bachelor's, or a bachelor's degree with at least five years of progressive experience in the specialty.

Mr. Joshi's academic credentials align with these criteria:

\begin{itemize}
	\item Mr. Joshi holds a \textbf{Master of Science in Information Systems} [Exhibit 5.1] from Touro College, New York. This qualifies as an advanced degree under EB2 guidelines.
	
	\item He also holds an MBA from \textbf{Bar Ilan University, Israel}, [Exhibit 5.2] with a specialization in cross-cultural business policies and global management, further enhancing his qualifications by demonstrating expertise in applying advanced knowledge to global financial strategies and policies.
\end{itemize}

USCIS recognizes membership in professional organizations as a potential indicator of exceptional ability under the \textbf{EB2 National Interest Waiver (NIW)}. According to 8 CFR § 204.5(k)(3)(ii)(F), this includes evidence of membership in associations requiring outstanding achievements or elite qualifications.

Mr. Joshi's qualifications align with this criterion:

\begin{itemize}
	\item \textbf{GAARP-FRM (Global Association of Risk Professionals -- Financial Risk Manager)} [Chapter 5 and Exhibit 8]: This globally recognized certification designates elite expertise in financial risk management, reflecting my exceptional capabilities in the field.
\end{itemize}

These certifications and Mr. Joshi's ongoing professional development through memberships and designations affirm his exceptional ability and demonstrate his standing within distinguished professional organizations.

USCIS guidelines under 8 CFR § 204.5(k)(3)(ii)(E) recognize authorship of scholarly articles in professional journals or major trade publications as evidence of exceptional ability. These publications must reflect contributions of major significance in the respective field.

Mr. Joshi's academic publications, as documented on \textbf{Google Scholar and other Premium Indexing} [Exhibit 4], meet this criterion by emphasizing the breadth and depth of his influence in advancing \textbf{quantitative modeling} and \textbf{risk analysis}:

\begin{itemize}
	\item \textbf{Citations}: His work has received a total of \textbf{500 citations}, showcasing its wide-reaching impact.
	
	\item \textbf{h-index of 12}: This indicates Mr. Joshi has at least 12 publications cited 12 or more times, reflecting consistent and meaningful contributions to my field.
	
	\item \textbf{i10-index of 15}: This demonstrates Mr. Joshi has 15 publications cited at least 10 times, underscoring the sustained relevance and influence of my research.
\end{itemize}

As documented on \textbf{Web of Science™} [Exhibit 4], Mr. Joshi's profile \url{https://www.webofscience.com/wos/author/rid/LWJ-0136-2024} reflects his commitment to advancing research in the fields of \textbf{computer science}, \textbf{engineering}, and \textbf{quantitative modeling}:

\begin{itemize}
	\item \textbf{Publications}: Mr. Joshi has authored \textbf{22 scholarly articles indexed in WoS}, of which \textbf{20 are indexed in the Web of Science Core Collection}, showcasing adherence to rigorous academic standards.
	
	\item \textbf{Research Metrics}:
	\begin{itemize}
		\item \textbf{H-Index of 3}: Demonstrates consistent contributions with at least three articles cited three or more times.
		\item \textbf{Sum of 19 Times Cited}: His work has been cited \textbf{19 times}, reflecting its relevance and application in academic and professional contexts.
		\item \textbf{Citing Patents}: One of his contributions has influenced intellectual property, with \textbf{one citation by a patent}, highlighting the practical utility of my research.
	\end{itemize}
	
	\item \textbf{Conferences and Journals}: Mr. Joshi's publications span premier conferences and technical journals, emphasizing critical advancements in \textbf{MEMS-based systems}, \textbf{secure multi-party computations}, and \textbf{nanotechnology-enhanced devices}.
\end{itemize}

Additionally, \textbf{Section C} are other sources of Mr. Joshi's research profile.

Under USCIS guidelines for the EB2 National Interest Waiver (NIW), Mr. Joshi's extensive experience spanning over 10 years, including roles at Bank of America, XL Catlin, and Genpact (Wells Fargo), qualifies him under the criteria outlined in 8 CFR § 204.5(k)(2) (advanced degree or equivalent) and 8 CFR § 204.5(k)(3)(ii)(F) (substantial contributions).

Mr. Joshi has developed and implemented advanced quantitative risk management tools and big data analytics, driving innovation and enhancing financial resilience in U.S. markets. Mr. Joshi's work aligns directly with national economic stability goals, making him a valuable asset under the NIW criteria.

\subsection{(ii) National Interest Waiver Justification}

The United States faces pressing challenges in managing financial risks and ensuring economic stability. According to \textbf{8 CFR § 204.5(k)}, to qualify for EB2 under \textbf{National Interest Waiver}, the applicant must demonstrate the potential to impact the national interest by contributing to areas like finance, technology, and education. Mr. Joshi's work addresses these critical issues by contributing to the national interest, as outlined by USCIS under \textbf{8 CFR § 204.5(k)} for the \textbf{EB2 National Interest Waiver}.

Below is a writeup of Mr. Joshi on this work:

\begin{itemize}
	\item \textbf{Enhancing Risk Resilience}: Through advanced financial modeling [section E(i)] and machine learning tools as evidenced through my work experience, I aim to mitigate financial crises and support national economic security. Financial resilience is a core element of the national interest, as seen in the government's focus on improving financial systems and predictive analysis as part of enhancing the \textbf{United States' global economic stability}. More details on this can be found at the U.S. Department of Treasury's Office of Financial Research: Financial Stability Oversight Council here: \url{https://home.treasury.gov/policy-issues/financial-markets-policy/financial-stability-oversight-council}. My work directly aligns with U.S. policy goals related to economic security and innovation, reinforcing the national significance of my contributions. The regulation can be found here: \url{https://www.ecfr.gov/current/title-8/chapter-I/part-204/subpart-A/section-204.5}.
	
	\item \textbf{Driving Innovation in Financial Analytics}: My application of big data technologies, including \textbf{Hadoop, Spark, and Kafka}, to financial analytics enhances \textbf{decision-making processes}---an essential national priority for ensuring the efficient flow of capital and minimizing risk within key financial sectors. The \textbf{National Science Foundation} (NSF) has prioritized innovation in \textbf{big data} technologies for better decision-making, as illustrated under the NSF's Big Data and Data Science Program: \url{https://www.nsf.gov/funding/pgm_summ.jsp?pims_id=504813}.
	
	\item \textbf{Educating the Workforce}: As an active educator [section E (iii)], I have equipped professionals in the financial sector with crucial skills to address systemic challenges, supporting an \textbf{innovative workforce} capable of overcoming dynamic financial challenges. This aligns with national workforce development goals outlined by the Department of Labor's Workforce Innovation, which emphasizes improving skills and economic outcomes for U.S. workers. More about this initiative can be found at the following link: \url{https://www.dol.gov/agencies/eta}.
\end{itemize}

Mr. Joshi's future endeavors and his future work has been shown in section E.

\textbf{Alignment with NIW Criteria}:
The contributions described above align with national objectives by supporting economic growth, resilience, and innovation in finance and related sectors. Mr. Joshi's qualifications align with the core intent of the \textbf{National Interest Waiver}: to benefit the United States in a significant manner. The unique combination of these qualifications and Mr. Joshi's ability to address critical financial and risk management challenges support his eligibility under the NIW criteria.

\begin{longtable}{|p{0.4\textwidth}|p{0.5\textwidth}|}
	\hline
	\textbf{Category (USCIS Reference)} & \textbf{Exhibit/Reference} \\
	\hline
	\textbf{8 CFR § 204.5(k)(2): Advanced Degree or Equivalent} & Master of Science in Information Systems (Exhibit 5), MBA from Bar Ilan University (Exhibit 5.1) \\
	\hline
	\textbf{8 CFR § 204.5(k)(3)(ii)(F): Publications in Professional Journals} & 305 citations, h-index of 12, i10-index of 15, Google Scholar (Exhibit 4.1) \\
	\hline
	\textbf{8 CFR § 204.5(k)(3)(ii)(E): Membership in Professional Organizations} & GAARP-FRM (Exhibit 8.1) \\
	\hline
	\textbf{8 CFR § 204.5(k)(2): Professional Experience} & 10+ years, including roles at Bank of America, XL Catlin, Genpact (Wells Fargo) \\
	\hline
	\textbf{8 CFR § 204.5(k)(3)(ii)(F): National Interest Impact} & Innovation in financial risk management, big data analytics, driving financial resilience, and workforce development \\
	\hline
\end{longtable}

\section{B. Professional Experience with US Banks and Contributions to Financial Stability}

This section summarizes my Extensive Experience Exceeding Ten Years.

\subsection{(i) Quantitative Risk Management at Bank of America (2019- Current)}

Mr. Joshi is currently employed as an AVP in the Global Risk \& Analytics division at Bank of America where he has played a pivotal role in developing and implementing quantitative models that support risk management functions as demonstrated in [Exhibit 3.1, 3.9, 10.1]. Bank of America, holding the second-largest portfolio of auto and home loans in the U.S., relies heavily on robust quantitative frameworks to ensure financial stability.

\textbf{Impact}: Mr. Joshi's contributions have directly mitigated systemic risks by ensuring compliance with stringent regulatory standards and providing robust tools for risk assessment also evidenced in [Exhibit 3.1, 3.9]. For example, during volatile market conditions in 2022, my big data analytics implementation used the bank's models successfully forecasted risk exposures, enabling preemptive actions that saved millions in potential losses. My meticulous reviews of model codes and implementation ensured accuracy, reducing potential operational and financial risks.

\textbf{Alignment with National Interests}

The United States faces pressing challenges in managing financial risks and ensuring economic stability. Mr. Joshi's work addresses these challenges by:

\begin{itemize}
	\item Enhancing Risk Resilience: Through advanced modeling and machine learning, Mr. Joshi has developed tools to preempt and mitigate financial crises. [Exhibit 4.5.1]
	
	\item Driving Innovation in Financial Analytics: By leveraging big data technologies, Mr. Joshi has developed more robust and efficient decision-making processes. [Exhibit 4.5.2]
	
	\item Educating the Workforce: Mr. Joshi's training initiatives have equipped professionals with the skills needed to navigate complex financial environments, fostering innovation and growth.
\end{itemize}

\subsection{(ii) Innovations in Monte Carlo Simulation and Validation at XL Catlin US Portfolio (2014-2015)}

At XL Catlin (now AXA), Mr. Joshi developed and validated stochastic models for a \$40 million portfolio, focusing on equity, fixed income, and alternative investments [Exhibit 3.8 and 10.2].

\textbf{Impact}: These efforts have strengthened asset valuation methodologies for the U.S.-based portfolios, ensuring precision in risk assessments and investment decisions. By emphasizing model validation and error rectification, he contributed to the stability of financial systems tied to U.S. markets, benefiting institutional and broader national economic structures.

\textbf{Alignment with NIW Criteria}: Demonstrates substantial merit, innovation, and measurable impact on economic systems critical to national interests.

\subsection{(iii) Innovations in Quantitative Modeling and Corporate Finance at Genpact End Client Wells Fargo Bank (2012-2014)}

In Mr. Joshi's role at \textbf{Genpact}, serving the \textbf{Wells Fargo Quantitative Corporate Finance team}, he spearheaded advanced analytics and automation initiatives to enhance quantitative modeling and corporate finance strategies [Exhibit 3.2, 3.3 and 10.3].

\textbf{Impact}: These innovations directly supported \textbf{Wells Fargo's corporate finance decisions}, particularly in \textbf{equity strategy} and \textbf{capital structure optimization}. By automating processes, enhancing model accuracy, and improving error-handling, I ensured greater efficiency and reduced errors by \textbf{30-50\%}, addressing approximately \textbf{20 weekly issues}, which resulted in improved operational robustness and more reliable financial analysis.

\textbf{Alignment with NIW Criteria}: This work demonstrates \textbf{substantial innovation} and the practical application of \textbf{advanced financial modeling and machine learning techniques}. It played a crucial role in supporting \textbf{critical U.S. financial markets}, with measurable benefits in efficiency, reliability, and accuracy, aligning with national interests by strengthening corporate finance practices.

\subsection{(iv) Big Data and Machine Learning Online Training at QcFinance 2011-2012 \& 2015-2016}

During his tenure at QcFinance India. [Exhibit 3.10 \& Exhibit 10.4], Mr. Joshi spearheaded big data training and implementations for financial startups in Manhattan. By integrating Hadoop and Spark ecosystems, he established real-time data lakes and machine learning pipelines. His notable achievements include:

\begin{itemize}
	\item Training over 100 professionals in advanced data science techniques, bridging the knowledge gap in big data analytics.
\end{itemize}

During a tenure at Qcfinance In, he created an architecture for machine learning solutions capable of handling live market feeds, enabling startups to optimize their trade decisions in real-time. These efforts not only support operational success but align directly with the national objective of financial systems innovation.

\subsection{Recommendation from past supervisors at different Banks}

To evidence the experience and work experience we have presented strong endorsements from industry and academic leaders highlighting expertise and significance of contributions. Letters from industry leaders and academic experts attesting to Mr. Joshi's contributions and their significance in Section C (iii) and Exhibit 3.

\section{C. Academic Contributions, Scholarly \& Industry Impact}
\subsection{Online Research Profiles}
The applicant's research contributions are documented on several platforms, including:
\begin{itemize}
	\item \textbf{ORCID}: 0009-0002-6011-5080
	\item \textbf{Web of Science}: ID LWJ-0136-2024
	\item \textbf{Scopus Author ID}: 7402524594
	\item \textbf{SSRN}: https://papers.ssrn.com/sol3/cf\_dev/AbsByAuth.cfm?per\_id=7372430
	\item \textbf{Google Scholar}: https://scholar.google.com/citations?user=jD8fpGMAAAAJ\&hl=en
	\item \textbf{ResearchGate}: https://www.researchgate.net/profile/Satyadhar-Joshi-2
	\item \textbf{Academia.edu}: https://bankofamerica.academia.edu/SatyadharJoshi
	\item \textbf{LinkedIn}: https://www.linkedin.com/in/satyadharjoshi/
\end{itemize}

\subsection{Google Scholar Profile}

\textbf{Google Scholar Profile} [Exhibit 2]

Mr. Joshi's academic contributions, documented on his Google Scholar profile, emphasize the breadth and depth of his influence in advancing quantitative modeling and risk analysis. With a total citation count of \textbf{494}, an \textbf{h-index of 12}, and an \textbf{i10-index of 17}.

His publications highlight significant contributions to the field and are frequently cited in leading research and regulatory circles globally [Exhibit 2].





\textbf{Impact of Research}

\begin{itemize}
	\item Mr. Joshi's total citation count reflects the extensive application and relevance of his work in key areas such as big data, distributed computing, financial risk modeling and distributed computing frameworks.
	
	\item Frequent citations and global conference invitations reflect international recognition of his significant contributions to theoretical and applied research.
	
	\item Noteworthy publications span multiple fields, underlining interdisciplinary value and their strategic importance for the national economy.
	
	\item Joshi won various awards for his achievement in the field of Gen AI for Finance and Risk [Exhibit 6.1,6.2] and was also awarded research grant award for applying High Performance Computing by Microsoft [Exhibit 6.3].
\end{itemize}

\subsection{(i) Highlighted Publications Journal Publications \& Book Chapters}


For first page of papers refer to Exhibit 4.

\subsection{(iii) Recommendation from industry experts showing appreciation and importance of Mr. Joshi's work}
Comments and applause by professionals on published research.

Mr. Joshi's work has been cited by various analysts at work. Use of Mr. Joshi's work by various analysts at different Banks. At Bank of America Mr. Roohi (double PhD) has praised his work [Exhibit 3]. Anshul Babbar [Exhibit 3] from NatWest and Ankit Gupta [Exhibit 3] from Royal Bank of Scotland, Gaurav Sharma (AXA) and other recommendations can be found.

\subsection{(iv) Books Published}

Books in published at various platforms [Exhibit 4]





\section{F. Exhibits and Attachments}

\begin{enumerate}
	\item \textbf{Exhibit 1:} Resume of Mr. Satyadhar Joshi  
	
	\item \textbf{Exhibit 2:} Research Profile – Google Scholar Profile Summary  
	
	\item \textbf{Exhibit 3:} Letters of Recommendation  
	\begin{itemize}
		\item Letters of Recommendation by Mr. Roohollah Hashemi  
		\item Letters of Recommendation by Mr. Ankit Gupta  
		\item Letters of Recommendation by Mr. Anshul Babbar  
		\item Letters of Recommendation by Mr. Gaurav Sharma  
		\item Letters of Recommendation by Mr. Nehal Jain  
		\item Letters of Recommendation by Mr. Rohan Boses 
	\end{itemize}
	
	\item \textbf{Exhibit 4:} Relevant Publications and Patents  
	\begin{itemize}
		\item First Papers of Research Papers, Books,  Certificates  
	\end{itemize}
	
	\item \textbf{Exhibit 5:} Academic Degrees and Evaluations  
	\begin{itemize}
		\item MS in IT, Touro College, New York City  
		\item MBA, Bar-Ilan University, Israel  
		\item BE in Electrical Engineering, RGTU, India  
	\end{itemize}
	
	\item \textbf{Exhibit 6:} Awards and Recognitions  
	\begin{itemize}
		\item Award by Global Recognition Awards (\url{www.globalrecognitionawards.org})  
		\item International Digital Innovation Award in "AI in Fin Risk" at the International Research Congress-2025 (\url{https://asiaresearchawards.com})  
		\item Microsoft Grand Student Award  
	\end{itemize}
	
	\item \textbf{Exhibit 7:}  Review and Editorial Acclaims
	
	\item \textbf{Exhibit 8:} Professional Certifications  
	\begin{itemize}
		\item FRM Certification  
	\end{itemize}
	
	\item \textbf{Exhibit 9:} Educator and Contributions for Upskilling Americans  
	\begin{itemize}
		\item Udemy Profile  
	\end{itemize}
	
	\item \textbf{Exhibit 10:} Ten Years Work Experience  
	\begin{itemize}
		\item Bank of America (April 2019 - Present)  
		\item XL Catlin (Aug 2014 - Aug 2015)  
		\item Genpact (Aug 2012 - Aug 2014)  
		\item QcFinance India (Aug 2011 - Aug 2012)  
	\end{itemize}
	
	\item \textbf{Exhibit 11:} H1B, W-2, Paystubs  
	
	\item \textbf{Exhibit 12:} Annual Reviews at Bank of America  
\end{enumerate}



\begin{center}
	\textbf{Evidence (RFE): USCIS I-140 Petition: Satyadhar Joshi}\\
	\textbf{Date: \today}
\end{center}

\vspace{1em}

\noindent
\textbf{To:}\\
USCIS\\



\noindent
\textbf{Subject:} Compliance with Dhansar Framework I-140 Immigrant Petition for Alien Worker (EB2-NIW)\\

Dear USCIS Officer,

\vspace{1em}

I am submitting this letter and the enclosed materials as an evidence regarding my I-140 Immigrant Petition (EB2-NIW), filed as Satyadhar Joshi. The deadline for this response is August 25, 2025.






\section*{Compliance with Dhanasar Framework}

I hereby confirm that this response fully addresses all three prongs of the \emph{Dhanasar} framework as follows:

\subsection*{Prong 1: Substantial Merit and National Importance}
The enclosed documentation demonstrates that my proposed endeavor: 

\textbf{Generative AI, Big Data, HPC (high perf computing) for financial risk modeling, workforce development and adoption strategies for US Competitiveness}

possesses substantial merit.  Several independent expert evaluations are included that validate both the significance of the proposed endeavor and my ongoing contributions in this field.			My submission includes a complete description, projections and impact of my proposed endeavor in the fields of Generative AI, Big Data, and High Performance Computing as applied to financial risk modeling, AI adoption and workforce development strategies. The materials demonstrate how this work carries substantial merit and national importance for the United States, particularly in strengthening US financial infrastructure and technological competitiveness.

\subsection*{Prong 2: Well-Positioned to Advance the Endeavor}
Also evidence that makes me among top 10-15\% researchers who possess this very specific niche expertise to implement the endeavor is presented. The evidence establishes my unique qualifications through and explained how my 10+ years of specialized experience at Bank of America (and other organization) and Advanced degrees in relevant fields (MS Information Systems, MBA) helps me implemented my endeavor. Recognition as peer reviewer for top financial technology journals on US Risk and AI US implementation. Independent experts letters reviewing my credentials and testimonials are included. 


\subsection*{Prong 3: National Benefit of Waiving Job Offer Requirement}
The submission proves waiver is in the national interest because PERM process would delay critical financial AI research. Immediate benefits outweigh labor market protections. Also, my work addresses urgent national priorities in financial security.



I respectfully request that USCIS review the attached materials and supporting evidence. I am confident that my response addresses all issues raised in the RFE. If any part of my response is unclear or if further information is required, please do not hesitate to contact me and I will promptly address and resolve any concerns.

Sincerely,\\


\textbf{Satyadhar Joshi}

Assistant Vice President Quant Analyst, BoFA	Mob: +1 929 356 5046 \\
Email: Satyadhar.Joshi@gmail.com













\section{E. Future Endeavors and Impact}

\subsection{(i) Future Work}

\begin{itemize}
	\item \textbf{Ongoing Research}: Mr. Joshi currently has published several papers in the field of enhancing financial risk management for strengthening integrity of US Financial system and currently has three papers under review in prominent financial journals, focusing on innovations in financial risk modeling, machine learning, and big data applications within finance. [Exhibit 4]
	
	\item \textbf{Internal Research with Bank of America}: Mr. Joshi also aims to continue to excel in his role at Bank of America, contributing to the development of advanced risk management models, improving financial system resilience, and ensuring compliance with U.S. financial regulations. [Exhibit 10]
	
	\item \textbf{Educational Initiatives}: Mr. Joshi is also committed to enhancing U.S. workforce skills by creating open educational resources such as tutorials and workshops, empowering individuals with practical knowledge in advanced financial analysis and data science to support national economic goals. [Exhibit 9]
\end{itemize}

\subsection{(ii) Future Work in Training: Empowering Veterans and Hard Working Americans: A Volunteer-Driven Initiative for Skills and Success}

As an educator and firm believer in the values of hard work, self-reliance, and personal responsibility, Mr. Joshi plans to expand his work as a nonprofit initiative to provide practical, skills-based education for U.S. veterans and dedicated individuals seeking to improve their lives [Exhibit 9 Teaching Profile]. This initiative reflects his commitment to honoring the service of those who have defended our freedoms and to strengthening America by equipping citizens with the tools to thrive in a competitive economy.

\subsubsection{A Mission to Honor Service and Build Independence}

This nonprofit is not about handouts but about empowering those who are ready to step up and invest in their own futures. It is guided by principles of patriotism and self-reliance:

\begin{itemize}
	\item \textbf{Veterans First}: Honoring the sacrifices of America's veterans by providing them with the skills and opportunities they need to succeed in civilian careers.
	
	\item \textbf{Empowering Hardworking Americans}: Offering tools and training to individuals willing to work hard and take responsibility for their success.
	
	\item \textbf{No Profit, Only Service}: This initiative is a nonprofit, volunteer-driven effort with no financial incentives---every resource and effort will be devoted to helping those who are ready to help themselves.
\end{itemize}

\subsubsection{Online Education for Practical Skills and Careers}

With a focus on delivering accessible, high-quality online training, this initiative will help individuals gain job-ready skills in fields critical to America's economy:

\begin{itemize}
	\item \textbf{Veteran-Focused Programs}: Tailored courses for veterans transitioning to civilian roles, emphasizing skills like data analysis, financial modeling, and technology.
	
	\item \textbf{Accessible Online Training}: Self-paced, results-driven courses available to anyone who is motivated to learn, ensuring flexibility for participants across the country.
	
	\item \textbf{Real-World Applications}: Every course and tutorial is designed to equip participants with practical knowledge they can immediately use to contribute to the workforce and their communities.
\end{itemize}

\subsubsection{Proven Success in Education}

Mr Joshi's experience as an online educator through platforms like Udemy [Exhibit 9.1] demonstrates his ability to deliver effective, results-oriented education.

\begin{itemize}
	\item \textbf{Merit-Based Learning}: Programs focus on equipping participants with marketable skills, not empty credentials.
	
	\item \textbf{Scalable Reach}: Online delivery ensures that thousands of individuals, regardless of location, can access training that rewards effort and ambition.
	
	\item \textbf{Veteran-Specific Curricula}: Courses tailored to help veterans translate their military discipline and experience into skills that align with the demands of modern industries.
\end{itemize}

\subsubsection{Volunteer-Driven and Community-Supported}

This initiative will be sustained through a network of volunteers, partnerships, and community support:

\begin{itemize}
	\item \textbf{Patriotic Partnerships}: Collaborating with organizations like the American Legion and Veterans of Foreign Wars (VFW) to connect with veterans and promote the program.
	
	\item \textbf{Volunteer Educators}: Enlisting professionals and industry experts who are passionate about giving back to train and mentor participants.
	
	\item \textbf{Community Sponsorships}: Partnering with local businesses and individuals who share a commitment to empowering hardworking Americans and honoring veterans.
\end{itemize}







\section{Future Endeavors and Impact}

The applicant's future work is focused on advancing financial risk management, enhancing workforce skills, and empowering underserved communities, particularly veterans and hardworking Americans. These initiatives align with the national interest by strengthening the U.S. economy, improving workforce readiness, and supporting national security through technological innovation and education.


\begin{itemize}
	\item \textbf{Ongoing Research for Knowledge Dissemination}: Mr. Joshi has published several papers in the field of financial risk management, contributing to the integrity of the U.S. financial system. He currently has over 10 pre-print papers focused on innovations in financial risk modeling, machine learning, and big data applications within finance, which he plans to publish in the next 1--2 years [Exhibit 4]
	
	\item \textbf{Internal Research with Bank of America}: Mr. Joshi also aims to continue to develop AI, Gen AI, Big Data, Devops in his role at Bank of America, contributing to the development of advanced risk management models, improving financial system resilience, and ensuring compliance with U.S. financial regulations and also helping bank provide effective and robust services. [Exhibit 10]
	
	\item \textbf{Educational Initiatives}: Mr. Joshi is also committed to enhancing U.S. workforce skills by creating open educational resources such as tutorials and workshops, empowering individuals with practical knowledge in advanced financial analysis and data science to support national economic goals. [Exhibit 9]
\end{itemize}

\subsection{Future Work in Training: Empowering Veterans and Hard Working Americans: A Volunteer-Driven Initiative for Skills and Success}

As an educator and firm believer in the values of hard work, self-reliance, and personal responsibility, Mr. Joshi plans to expand his work as a nonprofit initiative to provide practical, skills-based education for U.S. veterans and dedicated individuals seeking to improve their lives [Exhibit 9 Teaching Profile]. This initiative reflects his commitment to honoring the service of those who have defended our freedoms and to strengthening America by equipping citizens with the tools to thrive in a competitive economy.

\subsubsection{A Mission to Honor Service and Build Independence}

This nonprofit is not about handouts but about empowering those who are ready to step up and invest in their own futures. It is guided by principles of patriotism and self-reliance:

\begin{itemize}
	\item \textbf{Veterans First}: Honoring the sacrifices of America's veterans by providing them with the skills and opportunities they need to succeed in civilian careers.
	
	\item \textbf{Empowering Hardworking Americans}: Offering tools and training to individuals willing to work hard and take responsibility for their success.
	
	\item \textbf{No Profit, Only Service}: This initiative is a nonprofit, volunteer-driven effort with no financial incentives---every resource and effort will be devoted to helping those who are ready to help themselves.
\end{itemize}

\subsubsection{Online Education for Practical Skills and Careers}

With a focus on delivering accessible, high-quality online training, this initiative will help individuals gain job-ready skills in fields critical to America's economy:

\begin{itemize}
	\item \textbf{Veteran-Focused Programs}: Tailored courses for veterans transitioning to civilian roles, emphasizing skills like data analysis, financial modeling, and technology.
	
	\item \textbf{Accessible Online Training}: Self-paced, results-driven courses available to anyone who is motivated to learn, ensuring flexibility for participants across the country.
	
	\item \textbf{Real-World Applications}: Every course and tutorial is designed to equip participants with practical knowledge they can immediately use to contribute to the workforce and their communities.
\end{itemize}

\subsubsection{Proven Success in Education}

Mr Joshi's experience as an online educator through platforms like Udemy [Exhibit 9.1] demonstrates his ability to deliver effective, results-oriented education.

\begin{itemize}
	\item \textbf{Merit-Based Learning}: Programs focus on equipping participants with marketable skills, not empty credentials.
	
	\item \textbf{Scalable Reach}: Online delivery ensures that thousands of individuals, regardless of location, can access training that rewards effort and ambition.
	
	\item \textbf{Veteran-Specific Curricula}: Courses tailored to help veterans translate their military discipline and experience into skills that align with the demands of modern industries.
\end{itemize}

\subsubsection{Volunteer-Driven and Community-Supported}

This initiative will be sustained through a network of volunteers, partnerships, and community support:

\begin{itemize}
	\item \textbf{Patriotic Partnerships}: Collaborating with organizations like the American Legion and Veterans of Foreign Wars (VFW) to connect with veterans and promote the program.
	
	\item \textbf{Volunteer Educators}: Enlisting professionals and industry experts who are passionate about giving back to train and mentor participants.
	
	\item \textbf{Community Sponsorships}: Partnering with local businesses and individuals who share a commitment to empowering hardworking Americans and honoring veterans.
\end{itemize}


\subsection{Ongoing Research and Contributions at Bank of America}

The applicant is actively engaged in research and development in the field of financial risk management, with a focus on leveraging advanced technologies such as Generative AI, machine learning, and big data analytics. These efforts aim to enhance the resilience and integrity of the U.S. financial system.

\begin{itemize}
	\item \textbf{Ongoing Research}: The applicant has published several papers in the field of financial risk management and has three additional papers under review in prominent financial journals. These publications focus on innovations in financial risk modeling, machine learning, and big data applications within finance. The research contributes to the development of more robust and efficient risk management tools, which are critical for maintaining the stability of the U.S. financial system. [Exhibit 4.4]
	
	\item \textbf{Internal Research with Bank of America}: The applicant aims to continue excelling in their role at Bank of America by contributing to the development of advanced risk management models. These models will improve the resilience of the financial system and ensure compliance with U.S. financial regulations. The applicant's work directly supports national economic stability and security. [Exhibit 10.1]
\end{itemize}

\subsection{Educational and Research Initiatives inside and outside Workplace}

The applicant is committed to enhancing the skills of the U.S. workforce through educational initiatives that provide practical knowledge in advanced financial analysis, data science, and technology. These efforts align with national goals for workforce development and economic growth.

\begin{itemize}
	\item \textbf{Open Educational Resources}: The applicant plans to create and distribute open educational resources, including tutorials, workshops, and online courses, to empower individuals with the skills needed to thrive in a competitive economy. These resources will focus on advanced financial analysis, data science, and machine learning, ensuring that participants are equipped with marketable skills. [Exhibit 9.1]
	
	\item \textbf{Training Programs for Veterans and Hardworking Americans}: The applicant is developing a nonprofit initiative to provide practical, skills-based education for U.S. veterans and individuals seeking to improve their lives. This initiative reflects the applicant's commitment to honoring the service of veterans and strengthening America by equipping citizens with the tools to succeed in the modern economy.
\end{itemize}

\subsection{Empowering Veterans and Hardworking Americans}

The applicant's nonprofit initiative, **Empowering Veterans and Hardworking Americans**, is a volunteer-driven effort to provide accessible, high-quality education and training to underserved communities. This initiative is guided by principles of patriotism, self-reliance, and community support.

\subsubsection{Mission and Principles}

\begin{itemize}
	\item \textbf{Veterans First}: The initiative prioritizes the needs of U.S. veterans, providing them with the skills and opportunities necessary to transition successfully into civilian careers. By offering tailored courses in data analysis, financial modeling, and technology, the program helps veterans translate their military discipline and experience into valuable skills for the modern workforce.
	
	\item \textbf{Empowering Hardworking Americans}: The initiative offers tools and training to individuals who are willing to work hard and take responsibility for their success. The focus is on providing practical, job-ready skills that can be immediately applied in the workforce.
	
	\item \textbf{No Profit, Only Service}: This initiative is a nonprofit, volunteer-driven effort with no financial incentives. Every resource and effort is devoted to helping individuals who are ready to invest in their own futures.
\end{itemize}

\subsubsection{Online Education for Practical Skills}

The initiative will deliver accessible, high-quality online training programs designed to meet the needs of participants across the country:

\begin{itemize}
	\item \textbf{Veteran-Focused Programs}: Tailored courses for veterans transitioning to civilian roles, emphasizing skills such as data analysis, financial modeling, and technology. These programs are designed to help veterans succeed in high-demand industries.
	
	\item \textbf{Accessible Online Training}: Self-paced, results-driven courses available to anyone motivated to learn. The flexibility of online delivery ensures that participants from diverse backgrounds and locations can access the training.
	
	\item \textbf{Real-World Applications}: Every course and tutorial is designed to equip participants with practical knowledge that can be immediately applied in the workforce and their communities.
\end{itemize}

\subsubsection{Proven Success in Education}

The applicant's experience as an online educator through platforms like Udemy demonstrates their ability to deliver effective, results-oriented education. [Exhibit 9.1]

\begin{itemize}
	\item \textbf{Merit-Based Learning}: Programs focus on equipping participants with marketable skills, not empty credentials. The emphasis is on practical knowledge and real-world applications.
	
	\item \textbf{Scalable Reach}: Online delivery ensures that thousands of individuals, regardless of location, can access training that rewards effort and ambition.
	
	\item \textbf{Veteran-Specific Curricula}: Courses are tailored to help veterans translate their military discipline and experience into skills that align with the demands of modern industries.
\end{itemize}

\subsubsection{Volunteer-Driven and Community-Supported}

The initiative will be sustained through a network of volunteers, partnerships, and community support:

\begin{itemize}
	\item \textbf{Patriotic Partnerships}: Collaborating with organizations like the American Legion and Veterans of Foreign Wars (VFW) to connect with veterans and promote the program.
	
	\item \textbf{Volunteer Educators}: Enlisting professionals and industry experts who are passionate about giving back to train and mentor participants.
	
	\item \textbf{Community Sponsorships}: Partnering with local businesses and individuals who share a commitment to empowering hardworking Americans and honoring veterans.
\end{itemize}





\section{Conclusion}

The applicant's future endeavors in research, education, and workforce development align with the national interest by advancing financial risk management, enhancing workforce skills, and empowering underserved communities. These initiatives demonstrate the applicant's commitment to strengthening the U.S. economy and supporting national security through innovation and education. The applicant's contributions make them a valuable asset to the United States, fulfilling the criteria for an EB2 National Interest Waiver (NIW).


		\section{Introduction}	
	This comprehensive response addresses the Request for Evidence (RFE) dated May 28, 2025 regarding the Form I-140 petition for \textbf{Mr Satyadhar Joshi, also referred as Mr Joshi or the applicant}, currently Assistant Vice President in BoFA's Global Risk \& Analytics division. The response demonstrates how Mr. Joshi's work meets all three prongs of the \emph{Dhanasar} test while specifically addressing each deficiency noted by USCIS in the RFE. This consolidated response addresses the May 28, 2025 RFE for Satyadhar Joshi's EB2 NIW petition, combining:


\begin{itemize}
	\item Detailed proposed endeavor and why it is of substantial merit 
	\item Documents Supporting that Mr Joshi (applicant) is well positioned to implement  the endeavour 
	\item Specific rebuttals to all USCIS concerns
	\item Two LOR (Testimonials) and Independent Letters (From PhDs and University Professors)
	\item 100+ pages of supporting exhibits including selected publications, selected citations, downloads of Mr Joshi's (applicant) work
\end{itemize}



	
	Pursuant to the Request for Evidence (``RFE'') issued on May 28 2025, for \textbf{Mr. Joshi, the applicant}, whose petition for classification under the EB2 National Interest Waiver (``NIW'') category is pending with U.S. Citizenship and Immigration Services (``USCIS''). This memorandum addresses the RFE under the framework set forth in \textit{Matter of Dhanasar}, 26 I\&N Dec. 884 (AAO 2016), with evidence demonstrating Mr. Joshi's work and proposed en-devour \textbf{Generative AI, Big Data, HPC (high perf computing) for financial risk modeling, workforce development and adoption strategies for US Competitiveness} satisfies all three prongs: (1) substantial merit and national importance; (2) his unique position to advance the endeavor; and (3) the national benefit of waiving the job offer requirement. Mr Joshi's's 10 years of experience is very US specific and most of peer reviewed journal publications are US centric. We also submit a preponderance of evidence to further support the claim that Mr. Joshi ranks among the top 10-15\% in his proposed endeavor and domain, and that his endeavor is of substantial merit.
	
	
		% Add LOR Table and 4 Inv eval table on they focus
		% Add the pages again
	
	
\subsection{Job Description and SOC Code}

\begin{itemize}
	\item \textbf{Job Title:} Quantitative Research Analyst
	
	\item \textbf{SOC Code:} 13-2099.01 – Financial Quantitative Analysts (Closest Match)
	
	\item \textbf{Position Classification Rationale:} While the petitioner’s role aligns most closely with SOC Code 13-2099.01, this classification does not fully capture the interdisciplinary nature and national impact of his actual work. The petitioner operates at the intersection of generative AI development, regulatory compliance, systemic financial risk mitigation, and national workforce upskilling—functions that extend beyond the scope of any currently defined SOC code. This supports the conclusion that the job offer and PERM labor certification process are impractical and not aligned with the national interest.
	
	\item \textbf{Nontechnical Job Description:} The petitioner develops and applies advanced Big Data, Analytics and generative AI techniques to enhance financial risk models for use by U.S. banks, regulatory agencies, and academic institutions. His work improves the resilience, transparency, and efficiency of the national financial infrastructure. Additionally. He also takes part in workforce development initiatives in AI education, produces open-source regulatory compliance tools, and contributes to public-sector innovation through peer-reviewed research and advisory work.
\end{itemize}
Also attached the two pages with the new information : Exhibit~\ref{chap:i140}
	

	


\bibliographystyle{IEEEtran}
\bibliography{selfpprfe} % assumes selfpprfe.bib is your .bib file		
%\printbibliography[title={References}]


